Carbonate chemistry at Ny-Ålesund

### 2021-05-21 awipev-CO2.Rmd
fig AT vs S for paper

>>>>

# Same plot for paper
p_at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at))+
    labs(x="Salinity", y="Discrete AT")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
ggsave(filename = "figures/p_at_s.png", plot = p_at_s, width = 25, height = 20, units = "cm")
